Figure 3 normalization

### 2019-05-22 main_figures/figure3_normalization.Rmd
updated figure 3

ll <- list("Var in PCs 1-5 explained"=r3,
           "median ARI"=m,
           "ARI at true number of clusters"=m2)
chm(ll, scale="column", scaleTitle="z-score", value_format="%.2f", 
            sameScale=T, row_sortFn=function(x){ mean(x,na.rm=T) }, cluster_columns=FALSE)
```

>>>>

ll <- list("Var in PCs 1-5 explained"=r3,
           "median ARI"=m,
           "ARI at true number of clusters"=m2)
chm(ll, scale="column", scaleTitle="z-score", value_format="%.2f", 
            sameScale=TRUE, row_sortFn=function(x){ mean(x,na.rm=T) }, cluster_columns=FALSE)
```
